---
title: "Homework_6"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#HW Data
```{r}
library(ggplot2) # for graphics
library(MASS) # for maximum likelihood estimation

z <- rnorm(n=3000,mean=0.2)
z <- data.frame(1:3000,z)
names(z) <- list("ID","myVar")
z <- z[z$myVar>0,]
str(z)
summary(z$myVar)
```


This codes for some varibles to work with for learning about probabilities



```{r}
p1 <- ggplot(data=z, aes(x=myVar, y=..density..)) +
  geom_histogram(color="grey60",fill="cornsilk",size=0.2) 
print(p1)
```

this codes for a histogram to be produced with the data curated earlier, this has axis' labeled

```{r}
p1 <-  p1 +  geom_density(linetype="dotted",size=0.75)
print(p1)
```

this adds a dotted line fitted to the histogram created previously

```{r}
normPars <- fitdistr(z$myVar,"normal")
print(normPars)
str(normPars)
normPars$estimate["mean"] # note structure of getting a named attribute
```

This gives you a read out of the mean and the standard deviation of the created data set

```{r}
meanML <- normPars$estimate["mean"]
sdML <- normPars$estimate["sd"]

xval <- seq(0,max(z$myVar),len=length(z$myVar))

 stat <- stat_function(aes(x = xval, y = ..y..), fun = dnorm, colour="red", n = length(z$myVar), args = list(mean = meanML, sd = sdML))
 p1 + stat
 
```
 
this is giving you the mean probability of each possibly density point  

```{r}
expoPars <- fitdistr(z$myVar,"exponential")
rateML <- expoPars$estimate["rate"]

stat2 <- stat_function(aes(x = xval, y = ..y..), fun = dexp, colour="blue", n = length(z$myVar), args = list(rate=rateML))
 p1 + stat + stat2
```

this function adds an exponential curve for the probability of the created data

```{r}
stat3 <- stat_function(aes(x = xval, y = ..y..), fun = dunif, colour="darkgreen", n = length(z$myVar), args = list(min=min(z$myVar), max=max(z$myVar)))
 p1 + stat + stat2 + stat3
```

This adds a uniform distribution of the min and the max of the data( a straigt line)

```{r}
gammaPars <- fitdistr(z$myVar,"gamma")
shapeML <- gammaPars$estimate["shape"]
rateML <- gammaPars$estimate["rate"]

stat4 <- stat_function(aes(x = xval, y = ..y..), fun = dgamma, colour="brown", n = length(z$myVar), args = list(shape=shapeML, rate=rateML))
 p1 + stat + stat2 + stat3 + stat4
```

this code adds a line better fit then the mean probability line, this is because zeros are not taken into account

```{r}
xval <- seq(0,max(z$myVar+0.1),len=length(z$myVar))
pSpecial <- ggplot(data=z, aes(x=myVar/(max(myVar + 0.1)), y=..density..)) +
  geom_histogram(color="grey60",fill="cornsilk",size=0.2) + 
  xlim(c(0,1)) +
  geom_density(size=0.75,linetype="dotted")

betaPars <- fitdistr(x=z$myVar/max(z$myVar + 0.1),start=list(shape1=1,shape2=2),"beta")
shape1ML <- betaPars$estimate["shape1"]
shape2ML <- betaPars$estimate["shape2"]

statSpecial <- stat_function(aes(x = xval, y = ..y..), fun = dbeta, colour="orchid", n = length(z$myVar), args = list(shape1=shape1ML,shape2=shape2ML))
pSpecial + statSpecial
```

This is an example of the example data set with a beta probability line, this estimates the uncertainty of the dataset







#Practice data


```{r}
library(ggplot2)
library(MASS)
new_data<- read.table(file='./Data_Homework_6/JAEDataArchiveNewsomeRipple.csv' , header=TRUE, sep=",", comment.char="#")
str(new_data)

```

addition of data set from suggested website


```{r}
p1 <- ggplot(data=new_data, aes(x=CoyotePrice, y=..density..)) +
  geom_histogram(color="grey60",fill="cornsilk",size=0.2) 
print(p1)
```


```{r}
normPars <- fitdistr(new_data$CoyotePrice,"normal")
print(normPars)
str(normPars)
normPars$estimate["mean"] # note structure of getting a named attribute
```



```{r}
meanML <- normPars$estimate["mean"]
sdML <- normPars$estimate["sd"]

xval <- seq(0,max(new_data$CoyotePrice),len=length(new_data$CoyotePrice))

 stat <- stat_function(aes(x = xval, y = ..y..), fun = dnorm, colour="red", n = length(new_data$CoyotePrice), args = list(mean = meanML, sd = sdML))
 p1 + stat
```

#```{r}
stat3 <- stat_function(aes(x = xval, y = ..y..), fun = dunif, colour="darkgreen", n = length(new_data$CoyotePrice), args = list(min=min(new_data$CoyotePrice), max=max(new_data$CoyotePrice)))
 p1 + stat + stat2 + stat3
#```
```{r}
gammaPars <- fitdistr(new_data$CoyotePrice,"gamma")
shapeML <- gammaPars$estimate["shape"]
rateML <- gammaPars$estimate["rate"]

stat4 <- stat_function(aes(x = xval, y = ..y..), fun = dgamma, colour="brown", n = length(new_data$CoyotePrice), args = list(shape=shapeML, rate=rateML))
 p1+ stat4
```

Gamma fits this data the best.

# Simulate new data

```{r}
s<-rnorm(n=4680,mean=37.5)
s <- data.frame(1:4680,s)
names(s) <- list("A","B")
s <- s[s$B>0,]
str(s)
summary(s$B)
```

xval


```{r}
p2 <- ggplot(data=s, aes(x=B, y=..density..)) +
  geom_histogram(color="grey60",fill="cornsilk",size=0.2) 
print(p2)
```
```{r}
meanML <- normPars$estimate["mean"]
sdML <- normPars$estimate["sd"]

qval <- seq(0,max(s$B),len=length(s$B))


```


```{r}
gammaPars <- fitdistr(s$B,"gamma")
shapeML <- gammaPars$estimate["shape"]
rateML <- gammaPars$estimate["rate"]

stat4 <- stat_function(aes(x = qval, y = ..y..), fun = dgamma, colour="brown", n = length(s$B), args = list(shape=shapeML, rate=rateML))
 p2  + stat4
```