---
title: "Homework 8"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```



## This is an example of how the data would normally look.


This includes eyesize estimations from Stergas et al. 
```{r}
library(tidyverse)
library(ggplot2)
library(MASS)
library(dplyr)

# Example data set of Eye- Diameter at 72hpf
wt_e <- rnorm(n=100, mean=290 , sd=50)


null_e <-rnorm( n=100, mean=220 , sd=50)




eye_size_df <- data.frame(WTeyesize = wt_e , Nulleyesize = null_e)

str(eye_size_df)

long_df <- eye_size_df %>%
      pivot_longer(cols=WTeyesize:Nulleyesize, names_to= "Genotype" , values_to= "EyeSize")

head(long_df)

test<-t.test(wt_e,null_e, paired=TRUE)

print(test)

#p-value1(n=30): 5.8e-07, p-value(n=50):2.5e-09, p-value(n=100):2.2e-16

p1 <- ggplot(data=long_df, aes(x=Genotype, y=EyeSize)) + geom_point(color="white" , fill="purple", size=0.2) +
  stat_boxplot()

print(p1)








```


In retinal development the retina is finished being laminated by 72hpf, here we simulate data for a this time point, for organisms with proper lamination, leading to proper eye size (wt), and organisms missing a protein integral to eye development, causing improper lamination, and smaller eye size(null)


## Here we begin to adjust the means


```{r}
library(tidyverse)
library(ggplot2)
library(MASS)
library(dplyr)

# Example data set of Eye- Diameter at 72hpf
wt_e <- rnorm(n=30 , mean=270 , sd=50)


null_e <-rnorm( n=30 , mean=240 , sd=50)




eye_size_df <- data.frame(WTeyesize = wt_e , Nulleyesize = null_e)

str(eye_size_df)

long_df <- eye_size_df %>%
      pivot_longer(cols=WTeyesize:Nulleyesize, names_to= "Genotype" , values_to= "EyeSize")

head(long_df)

test<-t.test(wt_e,null_e, paired=TRUE)

print(test)

#p-value(250-240):0.2558 
#p-value(260-240):0.07137
#p-value(270-240):0.006474

p1 <- ggplot(data=long_df, aes(x=Genotype, y=EyeSize)) + geom_point(color="white" , fill="purple", size=0.2) +
  stat_boxplot()

print(p1)




```

 Adjusting the mean of each group to be values closer to eachother causes the groups to lose significant difference, moving up in groups of 10 we find that the means need to be 30 integers apart.


## Here we adjust the sample sizes


```{r}
library(tidyverse)
library(ggplot2)
library(MASS)
library(dplyr)

# Example data set of Eye- Diameter at 72hpf
wt_e <- rnorm(n=10 , mean=290 , sd=50)


null_e <-rnorm( n=10 , mean=240 , sd=50)




eye_size_df <- data.frame(WTeyesize = wt_e , Nulleyesize = null_e)

str(eye_size_df)

long_df <- eye_size_df %>%
      pivot_longer(cols=WTeyesize:Nulleyesize, names_to= "Genotype" , values_to= "EyeSize")

head(long_df)

test<-t.test(wt_e,null_e, paired=TRUE)

print(test)

#p-value(5):0.2921-0.2338
#p-value(10):0.07516-0.001271
#p-value(15):0.0001277

p1 <- ggplot(data=long_df, aes(x=Genotype, y=EyeSize)) + geom_point(color="white" , fill="purple", size=0.2) +
  stat_boxplot()

print(p1)




```


we find that the smallest sample size for an appropriate p-value would be a sample of 10 fish each, anything lower allows for significance to be lost